Paper Three Summary

### 2015-09-23 hw/read/3/summary.tex
formatting

\section*{Feature Extraction}
\begin{description}
\item[Hypotheses] The authors list two hypotheses \cite{bird09}: 
\begin{quote}
\emph{H1: Binaries that are developed by teams of engineers that are distributed will have more post-release failures than those developed by collocated engineers.}
\end{quote}
\begin{quote}
\emph{H2: Binaries that are distributed will be less complex, experience less code churn, and have fewer dependencies than collocated binaries.}
\end{quote}
\item[Future Work] The authors note that there haven't been any causal relationshisp established between development practices and effective distributed development. They suggest studies to examine the effects of various development practices on distributed development.
\end{description}

>>>>

\section*{Feature Extraction}
\begin{description}
\item [{Motivational~statements}] The motivation of this study was to compare the post release failures of Windows Vista components developed in a distributed fashion to those developed by collocated teams as to attain insight into the affect of distributed team development against collocated team development.
\item[Hypotheses] The authors list two hypotheses \cite{bird09}: 
\begin{quote}
\emph{H1: Binaries that are developed by teams of engineers that are distributed will have more post-release failures than those developed by collocated engineers.}
\end{quote}
\begin{quote}
\emph{H2: Binaries that are distributed will be less complex, experience less code churn, and have fewer dependencies than collocated binaries.}
\end{quote}
\item[Future Work] The authors note that there haven't been any causal relationshisp established between development practices and effective distributed development. They suggest studies to examine the effects of various development practices on distributed development.
\end{description}
